Main Analyses

### 2016-02-23 Rmd/main-analysis.Rmd
Separated figures onto new Rmd, and completely analysis up through weight selection as function of range in data relative to worst case.

setwd("~/Dropbox/publications/zambiaToff/private/zambiaToff/")
p_root <- getwd()
p_demand <- fp(p_root, "external/input_devel/demand/")
p_mod <- fp(p_root, "agroEcoTradeoff")
p_moddat <- fp(p_mod, "external/data/ZA")
p_figures <- full_path(p_root, "paper/figures/")
p_roads <- fp(p_root, "external/input_devel/roads")
p_roads2 <- paste0("/Users/lestes/Dropbox/data/zari/infrastructure/zambia/", 
                   "rda_dump/Final Shape files RDA/")
p_out <- fp(p_mod, "external/output")
```

```{r, eval = FALSE}
# roads
mgrid <- raster(fp(p_moddat, "ZA-mask.tif"))
load(fp(p_mod, "external/data/ZA/parks_roads.rda"))
zamroads <- readOGR(fp(p_roads, "osmroads/zamroadsfp.shp"), 
                    layer = "zamroadsfp")
roads <- zamroads
save(pas, roads, zambia, 
     file = full_path(p_mod, "external/data/ZA/parks_roads.rda"))

@@

# plot(ybdc$maize$heat)
# par(mfrow = c(1, 2))
# plot(ycost$maize$heat)
# plot(ycost$soy$heat)
# plot(ycost$both$heat)
# plot(bdc$both$heat)
# save(ybdc, cbdc, ycost, bdc, file = fp(p_out, "mainresults1502.rda"))
save(ybdc, ycost, bdc, file = fp(p_out, "mainresults1702.rda"))
# load(fp(p_out, "mainresults1402.rda"))
```

## Figures

How reconcilable are the different land use interests, and what would be the impacts of each?

I am using the two crops combined approach because there is little overlap between the two.

### Figure 1
```{r, eval = FALSE}
# select out results for "pure" cases (weight = 1)
pure <- sapply(cnames, function(x) which(round(ybdc$both$params[, x], 4) == 1))

fnames <- imp_sorter(fp(p_out, ybdc$both$bcode), inds = pure, fullnames = TRUE)
pure_r <- lapply(fnames, function(x) {  # x <- pure[1]
  DT <- cbind(fread(x), basedt[, .(x, y, convertible)])
  DTr <- dt_to_raster(DT, CRSobj)
})
# sapply(1:4, function(x) which(ps[, x] == 1))
# sum across crops and multiply by convertible areas
rs <- lapply(pure_r, function(x) calc(x[[1:2]], sum) * x[[3]])  # actual area
rs2 <- lapply(pure_r, function(x) calc(x[[1:2]], sum))  # conv pixels
# check
# sapply(rs, function(x) cellStats(x, sum))
# ybdc$both$optitab[ind %in% pure, Y]  # same, but C optimized out
# sapply(rs2, function(x) cellStats(x, sum))
# plot(pure_r[[3]])

# figure out overlaps between different pure objectives
pms <- expand.grid(rep(list(0:1), 4))[-1, ]  # logic grid
rownames(pms) <- 1:15
rs_over <- lapply(1:nrow(pms), function(x) {  # apply logic tests
  (rs2[[1]] == pms[x, 1]) & (rs2[[2]] == pms[x, 2]) & (rs2[[3]] == pms[x, 3]) &     (rs2[[4]] == pms[x, 4])
})
rs_overs <- stack(rs_over)

# legend to show class of overlap
pms$leg <- c("Y", "C", "YC", "Bd", "YBd", "BdC", "YBdC", "Ct", 
             "YCt", "CCt", "YCCt", "BdCt", "YBdCt", "CBdCt", 
             "YCBdCt")

# frequency of overlaps in different categories
# sum(pms[c(1, 3, 5, 7, 9, 11, 13, 15), "hist"])
pms$hist <- sapply(1:nlayers(rs_overs), function(x) {
  round(cellStats(rs_overs[[x]] * pure_r[[1]]$convertible, sum), 1)
})

# legend color
pms$col <- c("dodgerblue3", "goldenrod2", "tomato1", "yellow", 
             rep("tomato1", 2), "red3", "deepskyblue1", rep("tomato1", 2),
             rep("red3", 5))

# recode with unique number for overlap class, collapse to RasterLayer, 
# simplify classes for plotting
rs_over_rc <- stack(lapply(1:length(rs_over), function(x) rs_over[[x]] * x))
rs_over_rc <- calc(rs_over_rc, sum)
# plot(rs_over_rc == 6)
rclmat <- cbind(0:15, c(0, 1, 3, 5, 4, 5, 5, 6, 2, 5, 5, 6, 5, 6, 6, 6))
leg2 <- c("Yield", "Cost", "Carbon", "Biodiversity", "2 overlap", "3+ overlap")
rs_over_rc2 <- raster::reclassify(rs_over_rc, rclmat)

# plot(1:2, pch = 20, cex = 3, col = c("yellow", "yellow2"))

# For Panel B - impact statistics 
bpath <- fp(p_out, ybdc$both$bcode)
load(fp(bpath, "impacts_tab.rda"))  # get impacts table

# select out corresponding impact statistics, summarize
pure2 <- unlist(lapply(pure, function(x) c(x, x+1)))
vars <- c("iter", "conv_area", "tot_C", "fpa_conv", "mu_cost", "rarity",
          "priority",  "int_prior", "int_mean")
conv_stats <- selected_impacts(pure, fp(p_out, ybdc$both$bcode))
# conv_stats <- outtab[outtab$iter %in% pure, vars]
# conv_stats <- data.frame(t(sapply(pure, function(x) {  # x <- pure[1]
#   DF <- conv_stats[conv_stats$iter == x, ]
#   c(colSums(DF[, 2:4]), 
#     sapply(5:ncol(DF), function(y) weighted.mean(DF[, y], DF$conv_area)))
# }))) 
# colnames(conv_stats) <- vars[-1]

# rescale for common plot
svec <- c(100000, 10000000, 1000, 1, 0.1, 0.1, 0.1, 0.1)  # rescale factor
conv_stats_n <- sweep(as.matrix(conv_stats)[, -1], MARGIN = 2, svec, "/")
conv_stats_n <- conv_stats_n[, c(1, 4, 2, 6:ncol(conv_stats_n), 3)]

# Plots
# Panel A
# cols <- RColorBrewer::brewer.pal(11, "RdYlBu")
# cols <- colorspace::diverge_hsv(n = 11)
# colsi <- sapply(c(0.5, 0.75, 1), function(x) rgb(1, 1, 0.9, alpha = x))
cols <- c("dodgerblue3", "deepskyblue1", "goldenrod2", "yellow", "tomato1",
          "red3")
plot(1:6, pch = 20, cex = 3, col = cols)

tiff(fp(p_figures, "single_priorities.tif"), height = 3, width = 8, 
     units = "in", res = 300)
par(mfrow = c(1, 3))
imp_plot2(dtr = rs_over_rc2, impacts = i1, fpath = p_figures, 
          fnm = "pure_overlap", cexscale = 0.6, ftitle = "", crops = leg2, 
          stats = FALSE, cols = cols, hold = TRUE, marg = c(0, 0, 0, 0))

# Panel B
# totf <- cellStats(rs_over_rc > 0, sum)
par(mar = c(7, 4, 2, 2))
bp <- barplot(pms$hist / sum(pms$hist) * 100, ylim = c(0, 25), las = 2, 
              col = pms$col, mgp = c(2, 0.25, 0), tcl = -0.2, 
              ylab = "% converted area")
axis(side = 1, at = bp, labels = pms$leg, las = 2, mgp = c(2, 0.25, 0), 
     tcl = -0.2)
# TeachingDemos::subplot( 
#   bp <- barplot(pms$hist / sum(pms$hist) * 100, ylim = c(0, 25), las = 2, 
#                 col = pms$col, mgp = c(2, 0.25, 0), tcl = -0.2, 
#                 ylab = "% converted pixels", names.arg = pms$leg), 
#   x=grconvertX(c(0.1,0.45), from='npc'),
#   y=grconvertY(c(0.6,1), from='npc'),
#   type='fig', pars=list(mar=c(3,3,0,0) + 0.1))

# Panel C
# barplot(conv_stats_n)
blabs <- c("Area", "Time", "Carbon", "Priority", "Priority/intactness", 
           "Intactness", "Forest reserves")
# blabs <- sub(':', '\n', blabs)
tlabs <- c(expression(10^5~"km"^2), "hours", expression(10^7~"tons"), 
           rep("X10", 3), expression(10^3~"km"^2))
bp <- barplot(conv_stats_n, beside = TRUE, ylim = c(0, 14), las = 2, 
              col = pms$col[c(1, 2, 4, 8)], names.arg = rep("", length(blabs)), 
              ylab = "Impact*", mgp = c(2, 0.25, 0), tcl = -0.2)
text(x = bp[2, ] - 0.4, y = rep(-0.3, length(bp[1, ])), adj = 1, 
     labels = blabs, xpd = NA, srt = 90)
text(x = bp[3, ] + 0.4, y = rep(-0.3, length(bp[3, ])), adj = 1, 
     labels = tlabs, xpd = NA, srt = 90, cex = 0.8)
dev.off()

#### Need to redo pareto to pass in weighted mean function for all average 
#### costs (DONE)

## Figure 2 & 3 (probably supplemental)
```{r, eval = FALSE}
# yc_bdc_st <- as.matrix(stack(ycost$both$heat, bdc$both$heat) / 100)
# yc_bdc_st <- stack(ycost$both$heat, ycost$both$heat * 0, bdc$both$heat) / 100
# plot(ycost$both$heat > 1)
# plotRGB(yc_bdc_st, r = 1, g = 2, b = 3, colNA = "transparent", scale = 1)
# rgb(red = yc_bdc_st[, 1], rep(0, nrow(yc_bdc_st)), yc_bdc_st[, 2])
# plot(ycost$both$heat)

# individual maps
png(full_path(p_figures, "all-4-maps.png"), height = 7, width = 7, 
     units = "in", res = 300)
par(mfrow = c(2, 2))#, oma = c(0, 0, 0, 2))
ftitles <- c("Yield", "Carbon", "Biodiversity", "Cost")
legp <- c(TRUE, rep(FALSE, 3))
for(i in 1:4) {
  dtr <- calc(pure_r[[i]][[1:2]] * c(1, 2), sum)
  imp_plot2(dtr, impacts = i1, fpath = p_figures, fnm = "all-4-maps", 
            cexscale = 0.6, ftitle = ftitles[i], crops = c("maize", "soy"), 
            stats = FALSE, hold = TRUE, legend = legp[i], marg = c(0, 0, 2, 0))
}
dev.off()

# heat maps
implist <- list(ycost$both, bdc$both)
load(full_path(set_base_path(), paste0("external/data/ZA/parks_roads.rda")))
pacols <- c("transparent", "grey85", "grey75")
png(full_path(p_figures, "ycost-bdc-heat.png"), height = 400, width = 900)
par(mfrow = c(1, 2), oma = c(0, 0, 0, 2))
for(i in 1:2) {
  par(mar = c(1, 1, 1, 4))
  plot(zambia, col = "grey90", border = "transparent")
  ir <- implist[[i]]$heat
  ir[ir == 0] <- NA
  plot(ir, col = rev(heat.colors(20)), add = TRUE, )
  plot(pas[pas@data$type == "gma", ], add = TRUE, col = pacols[2],
       border = FALSE)
  plot(pas[pas@data$type == "npark", ], add = TRUE, col = pacols[3],
       border = FALSE)
  plot(roads, add = TRUE, lwd = 0.1, col = "grey")
}
dev.off()

## Figure 4

Value of just a bit of compromise

```{r, eval = FALSE}
p <- data.frame(ybdc$both$params)
outtab[1, ]
p[, c("Y", "C", "BD" ,"COST")] <- round(p[, c("Y", "C", "BD" ,"COST")], 2)
# scens <- list(c(0.9, 0.05, 0.05, 0), 
#               c(0.85, 0.05, 0.05, 0.05), 
#               c(0.1, 0.45, 0.45, 0.0), 
#               c(0.05, 0.45, 0.45, 0.05))
scens <- lapply(c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9), function(x) {
  c(1 - x, rep(x / 2, 2), 0)
})
# scens <- lapply(c(0, 0.15, 0.3, 0.45, 0.6, 0.75), function(x) {
#   c(1 - x, rep(x / 3, 3))
# })
pind <- sapply(scens, function(x) {
  x <- round(x, 2)
  which(p$Y == x[1] & p$C == x[2] & p$BD == x[3] & p$COST == x[4])
})

# select out impacts corresponding to those runs
cstats <- selected_impacts(pind, p_out, ybdc$both$bcode)

# check on selection
# il <- input_handler(p_moddat, crops[[1]])
# chk <- tradeoff_mod(targ, ybdc$both$params[pind[5], 7:10], 
#                     currprodmod = g, exist_list = il)
# DF <- data.frame(chk$impacts)
# outtab[outtab$iter == pind[5], -2]
# round(c(colSums(DF[, 2:4]),
#         sapply(5:ncol(DF), function(z) weighted.mean(DF[, z], DF$conv_area))), 
#       2)
# cstats[5, ]
outtab[outtab$iter == pind[5], ]
outtab[, 1:4][1:100,]

fnames <- dir(bpath, pattern = "csv")
fnames[pind[5]]

# calculate max impacts across both crops, and figure out the impact range, 
# and what percent that is relative to the worst case
allstats <- selected_impacts(1:nrow(p), p_out, ybdc$both$bcode)
minmaxstats <- allstats[, lapply(.SD, range)]
imp_range <- minmaxstats[, lapply(.SD, diff)]  # difference between best/worst
pct_of_tot <- minmaxstats[, lapply(.SD, function(x) diff(x) / max(x))]

dfunc <- function(x, y) 100 - y / x * 100
stnms <- names(cstats)[-1]
imp_pct <- cstats[, lapply(stnms, function(x) {
  dfunc(minmaxstats[[x]][2], get(x))
})]
setnames(imp_pct, stnms)

plot(imp_pct$tot_C, imp_pct$conv_area, type = "l", xlab = "", ylab = "", 
     axes = FALSE)        # xaxs = "r", yaxs = "r")

sctab <- do.call(rbind, scens) * 100
cx <- 0.7
lcols <- c("black", "red", "blue")
imp_pct[, {
  png(fp(p_figures, "weight_impact.png"), height = 4, width = 4, 
      units = "in", res = 300)
  par(mgp = c(2, 0.75, 0), mar = c(3, 3, 1, 1))
  plot(conv_area, tot_C, type = "l", xlab = "", ylab = "", #xaxt = "n", 
       axes = FALSE, ylim = c(0, 65), xlim = c(2, 12))#, xaxs = "r", yaxs = "r")
  lines(conv_area, int_prior, col = "red")
  lines(conv_area, mu_cost, col = "blue")
  axis(1, at = seq(2, 12, 1), cex = cx, cex.axis = cx, line = -0.25, 
       tcl = -0.2, mgp = c(1, 0.25, 0))
  axis(2, at = seq(0, 60, 5), las = 2, cex = cx, cex.axis = cx, line = -0.25, 
       tcl = -0.15, mgp = c(1, 0.25, 0))
  mtext("% land savings", side = 1, line = 1, cex = cx)
  mtext("% Carbon/Biodiv/Cost savings", side = 2, line = 1, cex = cx)
  inms <- c("tot_C", "int_prior", "mu_cost")
  for(i in 1:length(inms)) {
    text(conv_area[-1], get(inms[i])[-1], labels = sctab[-1, i + 1], 
         cex = cx * 0.8, pos = 3, offset = 0.2, col = lcols[i])
    text(conv_area[1] + 0.1, i, labels = 0, cex = cx * 0.8, pos = 3, 
         offset = i * 0.15 - 0.2, col = lcols[i])
  }
  legend("bottomleft", legend = c("Carbon", "Biodiv", "Cost"), cex = cx,
         text.col = lcols, col = lcols, bty = "n", lty = 1)
  dev.off()
}]

scens_r <- lapply(pind, function(x) {  # x <- pind[[1]]
  print(x)
  inm <- paste0(outtab[outtab$iter == x, "rc"][1], ".csv")
  fpath <- fp(fp(p_out, ybdc$both$bcode), inm)
  # fname <- dir(bpath, pattern = "csv", full.names = TRUE)[x]
  DT <- cbind(fread(fpath), basedt[, .(x, y, convertible)])
  DTr <- dt_to_raster(DT, CRSobj)
})

scens_rs2 <- lapply(scens_r, function(x) calc(stack(x[[1:2]]), sum))
# freq((rs2$Y + scens_rs2[[1]]) * scens_r[[1]]$convertible
# plot(scens_rs2[[1]] + scens_rs2[[2]])

# round(sapply(scens_rs2, function(x) {
#   cellStats(x * scens_r[[1]]$convertible * 100, sum)
# }))
# cstats$conv_area

# pms <- list(c(1, 2), c(1, 3), c(1, 4), c(1, 5))
# pms <- expand.grid(rep(list(0:1), 5))[-1, ]  # logic grid

# rasters showing overlap as weight is progressively put on C and BD
scens_over <- lapply(2:6, function(x) scens_rs2[[1]] + scens_rs2[[x]] * 2)

# overlap areas
scens_over_a <- sapply(1:length(scens_over), function(x) { # x <- 4
  sapply(1:3, function(y) {  # y <- 3
    r <- scens_over[[x]] == y
    # plot(r)
    round(cellStats(r * scens_r[[1]]$convertible, sum), 1)
  })
})
sum(scens_over_a[c(2, 3), 4])
# over_cols <- sapply(seq(0, 0.4, 0.1), function(x) rgb(1 - x, 0, x))
# par(mar = c(0, 0, 0, 0))
# plot(1:3, pch = 20, col = rgb(1, 0, 1))
# plot(zambia)

cols <- c("grey", c(rgb(0, 1, 0), rgb(0, 0, 1), rgb(1, 0, 1)))
ftits <- c("Y=0.9")
par(mfrow = c(1, 4))
for(i in 1:4) {
  plot(zambia)
  imp_plot2(scens_over[[i]], impacts = i1, fpath = p_figures, fnm = "bob", 
            col = cols, add = TRUE, 
            legend = FALSE)
}
plot(scens_over[[1]], col = c("transparent", over_cols[[5]]))
plot(scens_rs2[[1]])
plot(scens_over[[4]])
plot(calc(stack(scens_over), sum))

plot(calc(stack(scens_rs2[2:4]), sum))

ybdc$both$optimal[, {
  par(mfrow = c(2, 2), mar = rep(3, 4))
  hist(.SD, axes = FALSE, labels = FALSE)
}, .SDcol = 1:4]

frange <- function(x) diff(range(x)) / max(x)
fqtile <- function(x) diff(quantile(x, probs = c(0.025, 0.975))) / max(x) 
ybdc$both$optimal[, lapply(.SD, frange), .SDcol = 1:4]
ybdc$both$optimal[, lapply(.SD, fqtile), .SDcol = 1:4]

hist(ybdc$both$optimal$Y)

>>>>

setwd("~/Dropbox/publications/zambiaToff/private/zambiaToff/")
p_root <- getwd()
p_demand <- fp(p_root, "external/input_devel/demand/")
p_mod <- fp(p_root, "agroEcoTradeoff")
p_moddat <- fp(p_mod, "external/data/ZA")
p_figures <- full_path(p_root, "paper/figures/")
p_other <- fp(p_root, "external/input_devel/other/")
p_roads <- fp(p_root, "external/input_devel/roads")
p_roads2 <- paste0("/Users/lestes/Dropbox/data/zari/infrastructure/zambia/", 
                   "rda_dump/Final Shape files RDA/")
p_out <- fp(p_mod, "external/output")
```

```{r, eval = FALSE}
# roads
mgrid <- raster(fp(p_moddat, "ZA-mask.tif"))
load(fp(p_mod, "external/data/ZA/parks_roads.rda"))
zamroads <- readOGR(fp(p_roads, "osmroads/zamroadsfp.shp"), 
                    layer = "zamroadsfp")
roads <- zamroads
save(pas, roads, zambia, 
     file = full_path(p_mod, "external/data/ZA/parks_roads.rda"))
```

<a href="#top">Back to top</a>

@@

# plot(ybdc$maize$heat)
# par(mfrow = c(1, 2))
# plot(ycost$maize$heat)
# plot(ycost$soy$heat)
# plot(ycost$both$heat)
# plot(bdc$both$heat)
# save(ybdc, cbdc, ycost, bdc, file = fp(p_out, "mainresults1502.rda"))
save(ybdc, ycost, bdc, file = fp(p_out, "mainresults1702.rda"))
# load(fp(p_out, "mainresults1702.rda"))
```
<a href="#top">Back to top</a>
